---
title: "Workflow"
author: "Andrie de Vries"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DiagrammeR)
library(dplyr)
```

## Objective

We want to deploy a TensorFlow model to RStudio Connect that allows some end user code to get a prediction.


```{r usage_diagram_1, fig.height=2}
DiagrammeR("
  graph TD
    TF(TensorFlow API) --> U(User)
    U --> TF
")
```

## Complication

However, in reality the TensorFlow model needs the data in a very specific format, and we want the user to provide inputs in a simple format.

To solve this, you can put another API between the user and TensorFlow:


```{r usage_diagram_2, fig.height=2}
DiagrammeR("

  graph TD
  
    TF(TensorFlow API) --> API[Plumber API]
    API --> U(User)
    U --> API
    API --> TF

")
```

## Programming workflow

```{r programmer_worflow, fig.height=1}

DiagrammeR("
  graph LR
    TF[Train TensorFlow model] --> TF_API[Publish TensorFlow API]
    TF_API --> API[Deploy Plumber API]
")
```


## Workflow


```{r full_workflow, fig.height=2}
edge_relations <- tibble::tribble(
  ~from, ~to, ~rel, ~comment, ~fontcolor,
  1, 2, "deploy", NA,        "grey20",
  3, 4, "deploy", NA,        "grey20",
  2, 4, NA, "Numeric score", "blue",
  4, 2, NA, "Input matrix",  "red",
  4, 5, NA, "Class",         "blue",
  5, 4, NA, "Peptide",       "red"
) %>%
  mutate(
    id = 1:6
  )

edges_as_nodes <- tibble::tribble(
  ~x, ~y, ~label, ~shape,
  1.7, 2.5, "Peptide", "none",
  1.7, 1.5, "Input matrix", "none",
  2.3, 1.5, "Numeric score", "none",
  2.3, 2.5, "Class", "none"
) %>% 
  mutate(
    color = "transparent",
    fillcolor = "transparent",
    fontcolor = "blue",
    fontsize = 8
  )

node_df <- tibble::tribble(
  ~x, ~y, ~label, ~shape,
  1, 1, "Train TF model", "rectangle",  
  2, 1, "TensorFlow API", "oval", 
  1, 2, "R function", "rectangle",
  2, 2, "Plumber API", "oval", 
  2, 3, "User code", "oval"
) %>% 
  mutate(
    color = "aliceblue",
    fillcolor = "aliceblue",
    fontcolor = "black",
    fontsize = 10
  ) %>% 
  bind_rows(edges_as_nodes) %>% 
  mutate(
    id = seq_along(x),
    x = 2 * x,
    y = -y,
    fixedsize = FALSE
  )

create_graph(
  nodes_df = node_df,
  edges_df = edge_relations
) %>%
  set_edge_attr_to_display(attr = "rel") %>%
  # add_global_graph_attrs("inputscale", 0.75, "graph") %>%
  render_graph()
```
