---
title: "The reticulate package"
subtitle: "Integration of Python into R projects"
output: html_notebook
---

***

### Setup

```{r setup}
# Configure Python for reticulate BEFORE loading the package
Sys.setenv(RETICULATE_PYTHON = "/opt/python/3.12.3/bin/python3")

library(reticulate)

# Verify we're using the correct Python
cat("Python:", py_config()$python, "\n")

readr::write_csv(nycflights13::flights, "flights.csv")
cat("✓ Created flights.csv\n")
```

***

# From Python to R

### Use Python to manipulate data

```{r}
# Run Python code through reticulate
py_run_string("
import pandas
flights = pandas.read_csv('flights.csv')
flights = flights[flights['dest'] == 'ORD']
flights = flights[['carrier', 'dep_delay', 'arr_delay']]
flights = flights.dropna()
")

cat("✓ Python processed", nrow(py$flights), "rows\n")
```

### Use R to visualize Pandas DataFrame

```{r, fig.width=7, fig.height=3}
library(ggplot2)
cat("Rows in py$flights:", nrow(py$flights), "\n")
ggplot(py$flights, aes(carrier, arr_delay)) + geom_point() + geom_jitter()
```

***

# From R to Python

### Use R to read and manipulate data

```{r, message=FALSE}
library(tidyverse)
flights <- read_csv("flights.csv") %>%
  filter(dest == "ORD") %>%
  select(carrier, dep_delay, arr_delay) %>%
  na.omit()
cat("✓ R processed", nrow(flights), "rows\n")
```

### Use Python to print R dataframe

```{r}
# Access R's flights variable from Python
py_run_string("
import pandas as pd
print('✓ Python can access R data:')
print(r.flights.head(10))
")
```

***

See the [reticulate website](https://rstudio.github.io/reticulate/index.html) for details.

**Note:** This notebook uses `py_run_string()` to run Python code through reticulate, ensuring R and Python share the same session. This allows chunk-by-chunk execution in Positron.
